### 2020-08-05 Organismal_paper/Organismal_manuscript_and_code.Rmd
changes to discussion early paragraphs

*On the evolution of tentilla morphology* -- The evolutionary rate covariance results in [@damian2019evolution] indicate that tentilla are not only phenotypically integrated (with widespread evolutionary correlations across structures) but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues]. This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures. The rate covariance results are congruent with the evolutionary correlations we found (Fig. \@ref(figure8)). In addition, these evolutionary modules point to hypothetical functional modules. For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high-speed videos show that the involucrum helps direct the whiplash of the uncoiling cnidoband distally (towards the prey). The clade Tendiculophora contains far more species than its relatives Cystonectae, Apolemiidae, and Pyrostephidae. An increase in clade richness and ecological diversification can be triggered by a ‘key innovation’ [@simpson1955major]. The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification. A specific instance of this may have been the access to the abundant small crustacean prey such as copepods. The rapid darting escape response of copepods may preclude their capture in siphonophores without shooting cnidobands.

Siphonophore tentilla are beautifully complex and highly diverse. Our analyses show, however, that the siphonophore tentillum morphospace actually has a fairly low extant dimensionality due to having an evolutionary history with many synchronous, correlated changes. This can be due to many causes including structural constraints, shared developmental programs (by homology or proximity), or natural selection on separate developmental programs to preserve an adaptive function. A familiar example of functionally-maintained correlations between distinct structures can be found in maple trees, where leaf size, twig width, and branch spacing evolve in correlation to ensure that hydraulic supply and demand are balanced (Corner’s rules) [@ackerly1998leaf]. We believe some of the correlations we found are also maintained by natural selection to preserve a complex function across a wide variety of shapes and sizes. Most tentillum characters develop from a common bud (budding tentilla near the base of the tentacle),  and different nematocyst subtypes share a common evolutionary and developmental origin [@bode1988control;@david2008evolution]. In this sense, correlations within these modules are expected for reasons other than adaptive natural selection. However, we also found correlations between nematocyst and tentillum characters. Siphonophore tentacle nematocysts (in their cnidocytes) are not produced nor matured in the developing tentillum. These cnidocytes are produced by dividing cnidoblasts in the basigaster (basal swelling of the gastrozooid). Once the cnidocytes have assembled the nematocyst, they migrate outward along the tentacle [@carre1972study] and position themselves in the tentillum according to their type and size [@skaer1988formation]. Thus, the developmental programs that produce the observed nematocyst morphologies are spatially separated from those producing the tentillum morphologies, and they originate from evolutionarily distinct cell lineages. Therefore, we hypothesize the genetic correlations and phenotypic integration between tentillum and nematocyst characters are maintained through natural selection on separate regulatory networks, out of the necessity to work together and meet the spatial, mechanical, and functional constraints of their prey capture behavior. In order to adequately test these hypotheses, future work would need to study the genetic mechanisms underlying the development of tentilla from a comparative, evolutionary approach. Fortunately, the unique biology of siphonophore tentacles displays the full developmental sequence of tentilla along each tentacle, making siphonophores an ideal system for the comparative study of development.

>>>>

*On the evolution of tentilla morphology* -- Siphonophore tentilla are beautifully complex and highly diverse. Our new analyses show, however, that the siphonophore tentillum morphospace actually has a fairly low extant dimensionality due to having an evolutionary history with many synchronous, correlated changes. This can be due to many causes including structural constraints, shared developmental programs (by homology or proximity), or natural selection on separate developmental programs to preserve an adaptive function. Most tentillum characters develop from a common bud (budding tentilla near the base of the tentacle),  and different nematocyst subtypes share a common evolutionary and developmental origin [@bode1988control;@david2008evolution]. In this sense, correlations within these modules are expected for reasons other than adaptive natural selection. However, we also found correlations between nematocyst and tentillum characters. Siphonophore tentacle nematocysts (in their cnidocytes) are not produced nor matured in the developing tentillum. These cnidocytes are produced by dividing cnidoblasts in the basigaster (basal swelling of the gastrozooid). Once the cnidocytes have assembled the nematocyst, they migrate outward along the tentacle [@carre1972study] and position themselves in the tentillum according to their type and size [@skaer1988formation]. Thus, the developmental programs that produce the observed nematocyst morphologies are spatially separated from those producing the tentillum morphologies, and they originate from evolutionarily distinct cell lineages. Therefore, we hypothesize the genetic correlations and phenotypic integration between tentillum and nematocyst characters are maintained through natural selection on separate regulatory networks, out of the necessity to work together and meet the spatial, mechanical, and functional constraints of their prey capture behavior. In order to adequately test these hypotheses, future work would need to study the genetic mechanisms underlying the development of tentilla from a comparative, evolutionary approach. Fortunately, the unique biology of siphonophore tentacles displays the full developmental sequence of tentilla along each tentacle, making siphonophores an ideal system for the comparative study of development.

The evolutionary rate covariance results in [@damian2019evolution] indicated that tentilla are not only phenotypically integrated (with widespread evolutionary correlations across structures) but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues]. This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures. The rate covariance results are congruent with the evolutionary correlations we found (Fig. \@ref(figure8)). In addition, these evolutionary modules point to hypothetical functional modules. For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high-speed videos show that the involucrum helps direct the whiplash of the uncoiling cnidoband distally (towards the prey). The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification. A specific instance of this may have been the access to the abundant small crustacean prey such as copepods. The rapid darting escape response of copepods may preclude their capture in siphonophores without shooting cnidobands. Dietary diversification may be related to the far greater number of species in Tendicilophora than its relatives Cystonectae, Apolemiidae, and Pyrostephidae.
